### 2018-11-14 ms/ms_prosop.tex
updated pdf

	\renewcommand{\familydefault}{\sfdefault}\normalfont
	\centering
	\includegraphics[width=\columnwidth]{../reports/figures/brain_main_figure.png}
	\vspace*{-3mm}
  		\caption{Results of structural and functional brain imaging. A, inferior view of the cortical surface reconstructed from high-resolution structural MRI, depicting that the fusiform gyri show no sign of being abnormal; B, results for the “faces vs. landscapes” fMRI localizer task; C, results from the “faces vs. hands” fMRI localizer task. fMRI results are shown on the inflated cortical surface, with face activity shown in warm colors and activity for the respective control condition shown in cool colors. Results are thresholded at t=3. For both paradigms, strong bilateral activity can be seen for the face condition, in the lateral parts of the fusiform gyri. The anterior clusters in the fusiform gyri most likely correspond to the “fusiform face area” and the posterior clusters in the lateral occipital cortex most likely correspond to the “occipital face area”. Unthresholded normalized surface maps are available online: https://neurovault.org/collections/4017/.}%
  		\label{fig:brain}

@@

\begin{figure*}[htbp]
	\begin{minipage}{\textwidth}
		\renewcommand{\familydefault}{\sfdefault}\normalfont
		\centering
		\includegraphics[width=\columnwidth]{../reports/figures/cambridge_main_figure.png}
		\vspace*{-3mm}
		\caption{Results of Cambridge Face Memory Test (CFMT). JB shows perfect performance when one face needed to be remembered and recognized (1st part), but is among the slowest and most inaccurate participants when six faces had to be remembered and recognized (parts 2 and 3). Averaged over all three parts of the CFMT, JB answered 37 out of 72 items correctly (51\%). On average, the control participants answered 59 items correctly, (SD = 7), so to be within 2 SDs at least 45 hits are needed.}%
		\label{fig:cfmt}
	\end{minipage}
\end{figure*}

@@

	\renewcommand{\familydefault}{\sfdefault}\normalfont
	\centering
	\includegraphics[width=\columnwidth]{../reports/figures/famface_main_figure.png}
	\vspace*{-3mm}
	\caption{Results for the famous faces task. Face stimuli were grey-scaled and cut out with an ellipse so that only inner features were visible. For each face, three questions had to be answered: is the face familiar? (yes/no); from what context might that person be known? (politician, actor, musician, athlete, TV host); what is the name of the person? Results of the control participants (con) are shown in blue. JB's results for famous faces she did not preselect are shown in red and JB's results for faces which she previously picked as ones she thinks she can reliably recognize are shown in green (JB*). Picture of Barack Obama is in the public domain.}%
	\label{fig:famous}

@@

 \begin{figure*}[htbp]
 	\begin{minipage}{\textwidth}
 		\renewcommand{\familydefault}{\sfdefault}\normalfont
 		\centering
 		\includegraphics[width=\columnwidth]{../reports/figures/filterface_main_figure_mod.png}
 		\vspace*{-3mm}
 		\caption{Results for the filtered famous faces. Face stimuli were all shown in grey-scale and with peripheral features visible. The “original” condition consists of stimuli with no further manipulation; the high-pass filtered (HPF) version consists of faces which were filtered so that the edges of features are emphasized; the low-pass filtered (LPF) version consists of faces which were smoothed with a Gaussian kernel so that features are blurred and featural processing of faces is not possible. Each face has to be rated regarding familiarity, context and the person's name has to be given. Results of the control participants are shown in blue (con), JB's results for famous faces she did not preselect are shown in red and JB's results for faces which she previously listed as being recognizable are shown in green (JB*). Except for the familiarity ratings on HPF and LPF faces, where JB's performance is 2 SD below the controls, her performance on all tasks and for both preselected and not preselected faces was within the normal range. Picture of Barack Obama is in the public domain.}%
 		\label{fig:filtered}
 	\end{minipage}
 \end{figure*}

@@

	\renewcommand{\familydefault}{\sfdefault}\normalfont
	\centering
	\includegraphics[width=\columnwidth]{../reports/figures/emofaces_main_figure.png}
	\vspace*{-3mm}
 		\caption{Results of the emotion recognition task. In the task, one face was shown at a time (happy, angry, fearful, sad, disgusted, surprised or neutral) and had to be labeled in a 7-way forced-choice decision. The figure shows the percentage of correct responses for 17 unmatched male control participants in blue and for JB in red. JB scores 88\% correct, making her the second-best performing participant in the sample. Control data were taken from \citet{Wegrzyn_2017}; stimuli were taken from the NimStim database \citep{Tottenham_2009}.}%
	\label{fig:emo}

@@

In addition to identifying intentions and emotions, JB is also convinced that she can reliably judge the attractiveness of faces, and a number of episodes from her life seem to corroborate this impression.
In one episode, JB recalled being at a discotheque with a female friend. She saw a man she found handsome, had a drink with him and they talked for some amount of time. The other day, she was at a cafe with the same friend, as a man walked by. She remarked to her friend that he also looks quite handsome, to which her friend replied that this was the same man she had drinks with the night before. The same thing happened a third time, only a few days afterwards, with the same man, in pretty much the same way. This provides anecdotal evidence that JB's judgments of attractiveness are consistent across time.
JB also reported that she likes \textit{“odd”} faces and takes an immediate liking to anyone with some idiosyncratic features in their face. She finds people with green eyes or thick eyebrows immediately likable, predominantly because they are easier to identify and consequently interaction with them is considerably less stressful. \textit{“I like red hair a lot and take an immediate liking to anyone who has it”}, JB told us. Similarly, other cases of DP described in the literature have remarked that they focus on the “worst features” of each acquaintance's face to remember them, keep company with “physically distinctive” people and claim that forgetting someone's face should be regarded a compliment, because good looks are not memorable \citep{Fine_2012}.
Increasing the averageness of a face normally increases its perceived attractiveness \citep{Little_2011}) while making it less distinctive. Accordingly, we prepared a task where faces with different degrees of averageness were presented (Fig.~\ref{fig:attract}). In each trial a pair of faces was shown, one more and one less strongly averaged, and JB had to make a choice which one she finds more attractive or more likable. Compared to a group of 46 female control participants, JB showed a prototypical preference for more average faces when it comes to attractiveness, but was the only person in the group to find less average faces more likable. The results show that in DP, ratings of attractiveness and likability might dissociate (Fig.~\ref{fig:attract}, Fig.~\ref{fig:heat}). The findings are both in line with studies showing normal attractiveness ratings for individuals with DP \citep{Carbon_2010}, as well as the until now incompatible observation that they report liking 'odd' faces more.

@@

	\renewcommand{\familydefault}{\sfdefault}\normalfont
	\centering
	\includegraphics[width=\columnwidth]{../reports/figures/attract_main_figure.png}
	\vspace*{-3mm}
 		\caption{Results of the average faces task. The upper part of the figure shows a set of example stimuli, with the number of faces that were averaged to create the stimulus increasing from left to right. In the task, a random pair of faces was shown in each trial and the participants had to decide which one is more attractive (part 1) or more likable (part 2). The lower part of the figure shows the percentage of preferences for the more average face. If the average faces are preferred, the responses will lie above 50\%. If the less average faces are preferred, the responses will lie below 50\%. A response at exactly 50\% will indicate absence of a systematic preference of one over the other. Responses for 46 female control participants are shown in blue and results for JB are shown in red. Stimuli were created using faceresearch.org. Stimuli are based on images from \citet{DeBruine2017}, available under a CC-BY licence}%
 		\label{fig:attract}
\end{figure}

\begin{table*}[htbp]
	\renewcommand{\familydefault}{\sfdefault}\normalfont\renewcommand\thetable{1}
	\centering
	\caption{\bf Overview of JB's performance for all major tasks}
	\small
	\begin{tabular}{llllllll}
		\hline
			Domain & Test & \% correct & percentile & z & t & df & p \\
		\hline
		\multicolumn{2}{l}{Face recognition} \\
		& CFMT 1 &  100 &         73 &  0.61 &  0.59 &   26 &  0.561  \\
		& CFMT 2 &         37 &         \textbf{<1} & -3.53 & -3.40 &   26 &  0.002 \\
		& CFMT 3 &         33 &           \textbf{1} & -2.33 & -2.25 &   26 &  0.033  \\
		& Famous familiarity &         31 &          \textbf{<1} & -3.60 & -3.47 &   26 &  0.002 \\
		& Famous context &         58 &           \textbf{1} & -2.40 & -2.32 &   26 &  0.029 \\
		& Famous naming &         14 &           \textbf{1} & -2.39 & -2.31 &   26 &  0.029 \\
		\multicolumn{2}{l}{Face evaluation} \\
		& Emotion recognition &         88 &         87 &  1.15 &  1.08 &   16 &  0.294  \\
		& Eyes test &         72 &         21 & -0.81 & -0.80 &   49 &  0.425  \\
		& Attractiveness &         77 &         64 &  0.37 &  0.36 &   45 &  0.720 \\
		& Likability &         44 &          \textbf{<1} & -3.36 & -3.29 &   45 &  0.002 \\
		\multicolumn{2}{l}{Visuospatial} \\
		& BRLD-A &         33 &           \textbf{1} & -2.52 & -2.52 &  173 &  0.013 \\
		& BRLD-B &         38 &           \textbf{2} & -2.02 & -2.01 &  173 &  0.046 \\
		& LPS2-Visual &         48 &         16 & -1.00 & -1.00 &  128 &  0.321 \\
		\hline
	\end{tabular}
	\parbox{12cm}{\caption*{CFMT: Cambridge Face Memory Test \citep{Duchaine_2006cfmt}; Eyes test: Reading the mind in the eyes \citep{Baron_Cohen_2001}; BRLT: Bergen Right-Left Discrimination Test \citep{Ofte_2002}; LPS2-Visual: Leistungsprüfsystem 2 (“performance test system”), test of visuo-spatial skills \citep{Horn}. Bold-face numbers indicate a performance at least two standard deviations below the normative group's mean.} }
	\label{tab:summary}
\end{table*}

@@

	\renewcommand{\familydefault}{\sfdefault}\normalfont
	\centering
	\includegraphics[width=\columnwidth]{../reports/figures/overview_heatmap_mod.png}
	\vspace*{-3mm}
 		\caption{Comparison of JB's performance for all major tasks. Differences in z-scores for all pairings of tasks are reported, with positive scores indicating higher performance for the tasks listed in the rows, compared to the tasks listed in the columns. Differences larger than two standard deviations are highlighted by stronger colors and an annotation indicating the numerical difference in z-scores. The emerging pattern suggests that JB’s performance is impaired for tasks involving learning of multiple faces (CFMT 2 and 3), and the recognition of famous faces from their inner parts, compared to learning of a single face (CFMT 1) and the recognition of emotion, intention (Eyes test) and attractiveness in faces. CFMT: Cambridge Face Memory Test; Eyes test: Reading the mind in the eyes; BRLT: Bergen Right-Left Discrimination Test; LPS2-Visual: Leistungsprüfsystem 2 (“performance test system”), test of visuo-spatial skills.}%
 		\label{fig:heat}

@@

Regarding explanatory mechanisms for JB's deficits in unfamiliar and familiar face recognition, we expected that impaired configural processing might offer the best explanation. However, the present study as well as some previous work in the literature has found largely intact configural processing in DP \citep{Duchaine_2000, Le_Grand_2006}; but see \citet{Behrmann_2005} for contrary results). As we used uncropped images of faces including the peripheral features, one important question is whether testing configural processing of only the inner features of the face would have produced different results. Given the specificity of the disorder, it is reasonable to assume that in DP configural processing for other information (e.g. peripheral features) might be intact, and is impaired only for the inner features of the face. Indeed, two studies which investigated more general configural processing mechanisms found no deficits in DP \citep{Duchaine_2000, Le_Grand_2006}, while studies which used only the inner part of faces did find individuals with DP to be impaired \citep{Avidan_2011, Palermo_2011}. However, the fusiform gyrus is one potential neural correlate of the configural processing of faces \citep{Schiltz_2006}, and individuals with DP have mostly shown prototypical activity patterns \citep{Hasson_2003, Avidan_2005, Furl_2011}. In line with these observations, JB showed no structural or functional abnormalities in her fusiform gyri, at least on a macroanatomical scale. Therefore, the deficits in DP might manifest themselves higher up the face processing stream, for example in the anterior temporal areas responsible for matching a face to a person's identity \citep{Kriegeskorte_2007, Landi_2017}. These areas might constitute the neural basis for an impaired matching of novel face views with previously learned faces \citep{Duchaine_2000} in DP. Recognizing previously learned faces is highly variable in DP, and previous studies with famous faces already showed that hit rates were higher than would be expected from individuals who cannot recognize their parents or spouse \citep{Rivolta_2012, Garrido_2009}. For the first time, we showed that above-chance performance of individuals with DP in famous face tasks is not necessarily due to flukes or a function of familiarity. We hypothesize that these instances of successful recognition can be due to simple featural strategies that are not supposed to work for identity recognition, but sometimes do work nonetheless. For example, JB was able to recognize Mr. Obama by using a rare but simple-to-memorize combination of local features, like freckles on a dark complexion. Also, sometimes information from a different face-processing pathway, for example the pathway of processing expressions \citep{Haxby_2000, Calder_2005}, might be successfully exploited for identity recognition. For example, JB was able to recognize Ms. Merkel by information that is not identity-related but nevertheless stable over time, like a subtle facial expression that is present on most pictures of her.

>>>>

	\renewcommand{\familydefault}{\sfdefault}\normalfont
	\centering
	\includegraphics[width=\columnwidth]{../reports/figures/brain_main_figure.png}
	\vspace*{-3mm}
  		\caption{\textbf{Results of structural and functional brain imaging.} A, inferior view of the cortical surface reconstructed from high-resolution structural MRI, depicting that the fusiform gyri show no sign of being abnormal; B, results for the “faces vs. landscapes” fMRI localizer task; C, results from the “faces vs. hands” fMRI localizer task. fMRI results are shown on the inflated cortical surface, with face activity shown in warm colors and activity for the respective control condition shown in cool colors. Results are thresholded at t=3. For both paradigms, strong bilateral activity can be seen for the face condition, in the lateral parts of the fusiform gyri. The anterior clusters in the fusiform gyri most likely correspond to the “fusiform face area” and the posterior clusters in the lateral occipital cortex most likely correspond to the “occipital face area”. Unthresholded normalized surface maps are available online: https://neurovault.org/collections/4017/.}%
  		\label{fig:brain}

@@

\begin{figure*}[htbp]
	\begin{minipage}{\textwidth}
		\renewcommand{\familydefault}{\sfdefault}\normalfont
		\centering
		\includegraphics[width=\columnwidth]{../reports/figures/cambridge_main_figure.png}
		\vspace*{-3mm}
		\caption{\textbf{Results of the Cambridge Face Memory Test (CFMT).} JB shows perfect performance when one face needed to be remembered and recognized (1st part), but is among the slowest and most inaccurate participants when six faces had to be remembered and recognized (parts 2 and 3). Averaged over all three parts of the CFMT, JB answered 37 out of 72 items correctly (51\%). On average, the control participants answered 59 items correctly, (SD = 7), so to be within 2 SDs at least 45 hits are needed.}%
		\label{fig:cfmt}
	\end{minipage}
\end{figure*}

@@

	\renewcommand{\familydefault}{\sfdefault}\normalfont
	\centering
	\includegraphics[width=\columnwidth]{../reports/figures/famface_main_figure.png}
	\vspace*{-3mm}
	\caption{\textbf{Results for the famous faces task.} Face stimuli were grey-scaled and cut out with an ellipse so that only inner features were visible. For each face, three questions had to be answered: is the face familiar? (yes/no); from what context might that person be known? (politician, actor, musician, athlete, TV host); what is the name of the person? Results of the control participants (con) are shown in blue. JB's results for famous faces she did not preselect are shown in red and JB's results for faces which she previously picked as ones she thinks she can reliably recognize are shown in green (JB*). Picture of Barack Obama is in the public domain.}%
	\label{fig:famous}

@@

 \begin{figure*}[htbp]
 	\begin{minipage}{\textwidth}
 		\renewcommand{\familydefault}{\sfdefault}\normalfont
 		\centering
 		\includegraphics[width=\columnwidth]{../reports/figures/filterface_main_figure_mod.png}
 		\vspace*{-3mm}
 		\caption{\textbf{Results for the filtered famous faces.} Face stimuli were all shown in grey-scale and with peripheral features visible. The “original” condition consists of stimuli with no further manipulation; the high-pass filtered (HPF) version consists of faces which were filtered so that the edges of features are emphasized; the low-pass filtered (LPF) version consists of faces which were smoothed with a Gaussian kernel so that features are blurred and featural processing of faces is not possible. Each face has to be rated regarding familiarity, context and the person's name has to be given. Results of the control participants are shown in blue (con), JB's results for famous faces she did not preselect are shown in red and JB's results for faces which she previously listed as being recognizable are shown in green (JB*). Except for the familiarity ratings on HPF and LPF faces, where JB's performance is 2 SD below the controls, her performance on all tasks and for both preselected and not preselected faces was within the normal range. Picture of Barack Obama is in the public domain.}%
 		\label{fig:filtered}
 	\end{minipage}
 \end{figure*}

@@

	\renewcommand{\familydefault}{\sfdefault}\normalfont
	\centering
	\includegraphics[width=\columnwidth]{../reports/figures/emofaces_main_figure.png}
	\vspace*{-3mm}
 		\caption{\textbf{Results of the emotion recognition task.} In the task, one face was shown at a time (happy, angry, fearful, sad, disgusted, surprised or neutral) and had to be labeled in a 7-way forced-choice decision. The figure shows the percentage of correct responses for 17 unmatched male control participants in blue and for JB in red. JB scores 88\% correct, making her the second-best performing participant in the sample. Control data were taken from \citet{Wegrzyn_2017}; stimuli were taken from the NimStim database \citep{Tottenham_2009}.}%
	\label{fig:emo}

@@

In addition to identifying intentions and emotions, JB is also convinced that she can reliably judge the attractiveness of faces, and a number of episodes from her life seem to corroborate this impression.
In one episode, JB recalled being at a discotheque with a female friend. She saw a man she found handsome, had a drink with him and they talked for some amount of time. The other day, she was at a cafe with the same friend, as a man walked by. She remarked to her friend that he also looks quite handsome, to which her friend replied that this was the same man she had drinks with the night before. The same thing happened a third time, only a few days afterwards, with the same man, in pretty much the same way. This provides anecdotal evidence that JB's judgments of attractiveness are consistent across time.
JB also reported that she likes \textit{“odd”} faces and takes an immediate liking to anyone with some idiosyncratic features in their face. She finds people with green eyes or thick eyebrows immediately likable, predominantly because they are easier to identify and consequently interaction with them is considerably less stressful. \textit{“I like red hair a lot and take an immediate liking to anyone who has it”}, JB told us. Similarly, other cases of DP described in the literature have remarked that they focus on the “worst features” of each acquaintance's face to remember them, keep company with “physically distinctive” people and claim that forgetting someone's face should be regarded a compliment, because good looks are not memorable \citep{Fine_2012}.
Increasing the averageness of a face normally increases its perceived attractiveness \citep{Little_2011} while making it less distinctive. Accordingly, we prepared a task where faces with different degrees of averageness were presented (Fig.~\ref{fig:attract}). In each trial a pair of faces was shown, one more and one less strongly averaged, and JB had to make a choice which one she finds more attractive or more likable. Compared to a group of 46 female control participants, JB showed a prototypical preference for more average faces when it comes to attractiveness, but was the only person in the group to find less average faces more likable. The results show that in DP, ratings of attractiveness and likability might dissociate (Fig.~\ref{fig:attract}, Fig.~\ref{fig:heat}). The findings are both in line with studies showing normal attractiveness ratings for individuals with DP \citep{Carbon_2010}, as well as the until now incompatible observation that they report liking 'odd' faces more.

@@

	\renewcommand{\familydefault}{\sfdefault}\normalfont
	\centering
	\includegraphics[width=\columnwidth]{../reports/figures/attract_main_figure.png}
	\vspace*{-3mm}
 		\caption{\textbf{Results of the average faces task.} The upper part of the figure shows a set of example stimuli, with the number of faces that were averaged to create the stimulus increasing from left to right. In the task, a random pair of faces was shown in each trial and the participants had to decide which one is more attractive (part 1) or more likable (part 2). The lower part of the figure shows the percentage of preferences for the more average face. If the average faces are preferred, the responses will lie above 50\%. If the less average faces are preferred, the responses will lie below 50\%. A response at exactly 50\% will indicate absence of a systematic preference of one over the other. Responses for 46 female control participants are shown in blue and results for JB are shown in red. Stimuli were created using faceresearch.org. Stimuli are based on images from \citet{DeBruine2017}, available under a CC-BY licence.}%
 		\label{fig:attract}
\end{figure}

\begin{table*}[htbp]
	\renewcommand{\familydefault}{\sfdefault}\normalfont\renewcommand\thetable{1}
	\centering
	\caption{\bf Overview of JB's performance for all major tasks}
	\small
	\begin{tabular}{llllllll}
		\hline
			Domain & Test & \% correct & percentile & z & t & df & p \\
		\hline
		\multicolumn{2}{l}{Face recognition} \\
		& CFMT 1 &  100 &         73 &  0.61 &  0.59 &   26 &  0.561  \\
		& \textbf{CFMT 2} &    \textbf{37} &      \textbf{<1} & \textbf{-3.53} & \textbf{-3.40} &   \textbf{26} &  \textbf{0.002} \\
		& \textbf{CFMT 3} &    \textbf{33} &      \textbf{1} & \textbf{-2.33} & \textbf{-2.25} &   \textbf{26} &  \textbf{0.033}  \\
		& \textbf{Famous familiarity} &     \textbf{31} &      \textbf{<1} & \textbf{-3.60} & \textbf{-3.47} &   \textbf{26} &  \textbf{0.002} \\
		& \textbf{Famous context} &     \textbf{58} &        \textbf{1} & \textbf{-2.40} & \textbf{-2.32} &   \textbf{26} &  \textbf{0.029} \\
		& \textbf{Famous naming} &      \textbf{14} &        \textbf{1} & \textbf{-2.39} & \textbf{-2.31} &   \textbf{26} &  \textbf{0.029} \\
		\multicolumn{2}{l}{Face evaluation} \\
		& Emotion recognition &         88 &         87 &  1.15 &  1.08 &   16 &  0.294  \\
		& Eyes test &         72 &         21 & -0.81 & -0.80 &   49 &  0.425  \\
		& Attractiveness &         77 &         64 &  0.37 &  0.36 &   45 &  0.720 \\
		& \textbf{Likability} &         \textbf{44} &          \textbf{<1} & \textbf{-3.36} & \textbf{-3.29} &   \textbf{45} &  \textbf{0.002} \\
		\multicolumn{2}{l}{Visuo-spatial} \\
		& \textbf{BRLD-A} &         \textbf{33} &       \textbf{1} & \textbf{-2.52} & \textbf{-2.52} &  \textbf{173} &  \textbf{0.013} \\
		& \textbf{BRLD-B} &         \textbf{38} &       \textbf{2} & \textbf{-2.02} & \textbf{-2.01} &  \textbf{173} &  \textbf{0.046} \\
		& LPS2-Visual &         48 &         16 & -1.00 & -1.00 &  128 &  0.321 \\
		\hline
	\end{tabular}
	\parbox{12cm}{\caption*{CFMT: Cambridge Face Memory Test \citep{Duchaine_2006cfmt}; Eyes test: Reading the mind in the eyes \citep{Baron_Cohen_2001}; BRLT: Bergen Right-Left Discrimination Test \citep{Ofte_2002}; LPS2-Visual: Leistungsprüfsystem 2 (“performance test system”), test of visuo-spatial skills \citep{Horn}. Bold-face text indicates a performance at least two standard deviations below the normative group's mean.} }
	\label{tab:summary}
\end{table*}

@@

	\renewcommand{\familydefault}{\sfdefault}\normalfont
	\centering
	\includegraphics[width=\columnwidth]{../reports/figures/overview_heatmap_mod.png}
	\vspace*{-3mm}
 		\caption{\textbf{Comparison of JB's performance for all major tasks.} Differences in z-scores for all pairings of tasks are reported, with positive scores indicating higher performance for the tasks listed in the rows, compared to the tasks listed in the columns. Differences larger than two standard deviations are highlighted by stronger colors and an annotation indicating the numerical difference in z-scores. The emerging pattern suggests that JB’s performance is impaired for tasks involving learning of multiple faces (CFMT 2 and 3), and the recognition of famous faces from their inner parts, compared to learning of a single face (CFMT 1) and the recognition of emotion, intention (Eyes test) and attractiveness in faces. CFMT: Cambridge Face Memory Test; Eyes test: Reading the mind in the eyes; BRLT: Bergen Right-Left Discrimination Test; LPS2-Visual: Leistungsprüfsystem 2 (“performance test system”), test of visuo-spatial skills.}%
 		\label{fig:heat}

@@

Regarding explanatory mechanisms for JB's deficits in unfamiliar and familiar face recognition, we expected that impaired configural processing might offer the best explanation. However, the present study as well as some previous work in the literature has found largely intact configural processing in DP (\citet{Duchaine_2000, Le_Grand_2006}; but see \citet{Behrmann_2005} for contrary results). As we used uncropped images of faces including the peripheral features, one important question is whether testing configural processing of only the inner features of the face would have produced different results. Given the specificity of the disorder, it is reasonable to assume that in DP configural processing for other information (e.g. peripheral features) might be intact, and is impaired only for the inner features of the face. Indeed, two studies which investigated more general configural processing mechanisms found no deficits in DP \citep{Duchaine_2000, Le_Grand_2006}, while studies which used only the inner part of faces did find individuals with DP to be impaired \citep{Avidan_2011, Palermo_2011}. However, the fusiform gyrus is one potential neural correlate of the configural processing of faces \citep{Schiltz_2006}, and individuals with DP have mostly shown prototypical activity patterns \citep{Hasson_2003, Avidan_2005, Furl_2011}. In line with these observations, JB showed no structural or functional abnormalities in her fusiform gyri, at least on a macroanatomical scale. Therefore, the deficits in DP might manifest themselves higher up the face processing stream, for example in the anterior temporal areas responsible for matching a face to a person's identity \citep{Kriegeskorte_2007, Landi_2017}. These areas might constitute the neural basis for an impaired matching of novel face views with previously learned faces \citep{Duchaine_2000} in DP. Recognizing previously learned faces is highly variable in DP, and previous studies with famous faces already showed that hit rates were higher than would be expected from individuals who cannot recognize their parents or spouse \citep{Rivolta_2012, Garrido_2009}. For the first time, we showed that above-chance performance of individuals with DP in famous face tasks is not necessarily due to flukes or a function of familiarity. We hypothesize that these instances of successful recognition can be due to simple featural strategies that are not supposed to work for identity recognition, but sometimes do work nonetheless. For example, JB was able to recognize Mr. Obama by using a rare but simple-to-memorize combination of local features, like freckles on a dark complexion. Also, sometimes information from a different face-processing pathway, for example the pathway of processing expressions \citep{Haxby_2000, Calder_2005}, might be successfully exploited for identity recognition. For example, JB was able to recognize Ms. Merkel by information that is not identity-related but nevertheless stable over time, like a subtle facial expression that is present on most pictures of her.
